\documentclass[12pt]{article}
%\usepackage[vmargin=1.5cm, hmargin=1.5cm]{geometry}                
%\geometry{letterpaper}           
\usepackage[letterpaper, margin=1.87cm]{geometry}
%\usepackage{times}
\usepackage{graphicx, hanging, mdwlist, titlesec}
\usepackage{amssymb, fancyhdr, enumitem}
\usepackage{threeparttable, subfigure, multirow}
\usepackage{hyperref}
\usepackage{tikz}


%Header
\renewcommand{\headrulewidth}{0pt} 
\fancyhf{}
\lhead{\textbf{Ken A. Thompson} \textit{CV}}
\rhead{\thepage}

\setitemize{noitemsep, topsep=1pt} %space bw items and bw paras and items in itemize enviro
\titlespacing{\subsection}{0pt}{*1}{*0}

\newcommand*{\ClipSep}{0.4cm}%

\begin{document}
\thispagestyle{empty} 
\pagestyle{fancy}

% Defines the rSection environment for the large sections within the CV
\newenvironment{rSection}[1]{ % 1 input argument - section name
  \sectionskip
  \MakeUppercase{\bf #1} % Section title
  \sectionlineskip
  \hrule % Horizontal line
  \vspace{0.25em} % Some space after the list of bullet points
}

% The below commands define the whitespace after certain things in the document
\def\namesize{\huge} % Size of the name at the top of the document
\def\addressskip{\smallskip} % The space between the two address (or phone/email) lines
\def\sectionlineskip{\smallskip} % The space above the horizontal line for each section 
\def\nameskip{\bigskip} % The space after your name at the top
\def\sectionskip{\medskip} % The space after the heading section


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\begin{center}
{\raggedleft
\noindent\Large{\textbf{KEN A.\ THOMPSON}}\\
\large Ph.D. Candidate\\
\large Zoology Dept. \& Biodiversity Research Centre \\
\large University of British Columbia \\
\large ken.thompson@zoology.ubc.ca\\
\href{https://ecolutionaryevology.com}{ecolutionaryevology.com}\\
%\end{center}
}

%%%%%%%%%%%%%%%%%%%%%%%%%
%	EDUCATION SECTION   %
%%%%%%%%%%%%%%%%%%%%%%%%%

\noindent\begin{rSection}{Education}
\vspace{0.25em}

{\bf Ph.D.} \hfill {\em September 2016 - Present} 
\\ University of British Columbia \hfill { Supervisor: Dolph Schluter }
\\ Department of Zoology \\

\\{\bf M.Sc.} \hfill {\em September 2014 - July 2018} 
\\ University of Toronto\hfill { Supervisor: Marc T.J. Johnson }
\\ Department of Ecology & Evolutionary Biology \\

\\{\bf B.Sc. Hon.} \hfill {\em September 2010 - April 2014} 
\\ University of Guelph\hfill { Supervisors: Brian C. Husband \& Hafiz Maherali }
\\ Department of Integrative Biology \\

\end{rSection}

%%%%%%%%%%%%%
%	PUBZ   %
%%%%%%%%%%%%

\noindent\begin{rSection}{Publications}

% \vspace{0.25em}
\subsubsection*{Pre-prints}

\hangpara{1cm}{1}\noindent\hspace{.1cm}1. Santangelo JS, Avenard C, Rivkin LR, and \textbf{Thompson KA}. Multivariate phenotypic divergence along an urbanization gradient. bioRχiv, 699017.

\hangpara{1cm}{1}\noindent\hspace{.1cm}2. Santangelo JS, \textbf{Thompson KA}, Cohan, B, Syed J, Ness, RW, and MTJ Johnson. Predicting the strength of urban-rural clines in a Mendelian polymorphism along a latitudinal gradient. bioRχiv, 635763.

\subsubsection*{Peer-reviewed}

\hangpara{1cm}{1}\noindent\hspace{.1cm}13. \textbf{Thompson KA}, Osmond MM, Schluter D. 2019. Parallel genetic evolution and speciation from standing variation. \textit{Evolution Letters} 3(2):129-141. doi: 10.1002/evl3.106

\hangpara{1cm}{1}\noindent\hspace{.1cm}12. Rivkin LR, Santangelo JS, Alberti M, Aronson MFJ, de Keyzer CW, Diamond SE, Fortin M-J, Frazee LD, Gorton AJ, Hendry AP, Liu Y, Losos JB, MacIvor JS, Martin RA, McDonnell MJ, Miles LS, Munshi-South J, Ness RW, Newman AEM, Stothart M, Theodorou P, \textbf{Thompson KA}, Verrelli BC, Whitehead A, Winchell KM and MTJ Johnson. 2019. A roadmap for urban evolutionary ecology. \textit{Evolutionary Applications} 12(3): 384–398. doi: 10.1111/eva.12734.

\hangpara{1cm}{1}\noindent\hspace{.1cm}11. Santangelo JS, \textbf{Thompson KA} and MTJ Johnson. 2019. Herbivores and plant defenses affect selection on plant reproductive traits more strongly than pollinators. Journal of Evolutionary Biology 32: 4–18. doi: 10.5061/dryad.h6qg003.
(ESEB Stearns Prize winner for best graduate student paper [to JSS])

\hangpara{1cm}{1}\noindent\hspace{.1cm}10. \textbf{Thompson KA}, Rieseberg LH and D Schluter. 2018. Speciation and the city. Trends in Ecology & Evolution 33(11): 815–826. doi: 10.1016/j.tree.2018.08.007

\hangpara{1cm}{1}\noindent\hspace{.1cm}9. \textbf{Thompson KA}, KA Cory and MTJ Johnson. 2017. Induced defenses alter the strength and direction of natural selection on plant reproductive traits in common milkweed. Journal of Evolutionary Biology. 30(6): 1219–1228. doi: 10.1111/jeb.13045.

\hangpara{1cm}{1}\noindent\hspace{.1cm}8. \textbf{Thompson KA}, M Renaudin and MTJ Johnson. 2016. Urbanization drives the evolution of parallel clines in plant populations. Proceedings of the Royal Society of London B: Biological Sciences. 20162180. doi: 10.1098/rspb.2016.2180.

\hangpara{1cm}{1}\noindent\hspace{.1cm}7. \textbf{Thompson KA} and MTJ Johnson. 2016. Antiherbivore defenses alter natural selection on plant reproductive traits. Evolution 70(4): 796–810. doi: 10.1111/evo.12900.

\hangpara{1cm}{1}\noindent\hspace{.1cm}6. Johnson MTJ, \textbf{Thompson KA} and HS Saini. 2015. Plant evolution in the urban jungle. American Journal of Botany 102(12): 1–3. doi: 10.3732/ajb.1500386

\hangpara{1cm}{1}\noindent\hspace{.1cm}5. Oke OA and KA Thompson. 2015. Distribution models for mountain plant species: the value of elevation. Ecological Modelling 301, 72–77. doi:10.1016/j.ecolmodel.2015.01.019

\hangpara{1cm}{1}\noindent\hspace{.1cm}4. \textbf{Thompson KA}, BC Husband and H Maherali. 2015. No influence of water limitation on the outcome of competition between diploid and tetraploid \textit{Chamerion angustifolium}m (Onagraceae). Journal of Ecology 103(3), 733–741. doi: 10.1111/1365-2745.12384

\hangpara{1cm}{1}\noindent\hspace{.1cm}3. \textbf{Thompson KA}, BC Husband and H Maherali. 2014. Climatic niche differences between diploid and tetraploid cytotypes of \textit{Chamerion angustifolium} (Onagraceae). American Journal of Botany 101(11) 1868–1875. doi: 10.3732/ajb.1400184 

\hangpara{1cm}{1}\noindent\hspace{.1cm}2. \textbf{Thompson KA} and SG Newmaster. 2014. Molecular taxonomic tools provide more accurate estimates of species richness at less cost than traditional morphology-based taxonomic practices in a vegetation survey. Biodiversity and Conservation 23(6): 1411–1424. doi: 10.1007/s10531-014-0672-z

\hangpara{1cm}{1}\noindent\hspace{.1cm}1. \textbf{Thompson KA}, DS Sora, KA Cross, JM St. Germain and K Cottenie. 2014. Mucilage reduces leaf herbivory in Schreber’s water shield, \textit{Brasenia schreberi} J. F. Gmel. (Cabombaceae). Botany 92(5): 412–416. doi: 10.1139/cjb-2013-0296
(NRC Press Editor’s Choice Selection)

\vspace{0.5em} % Some space after the list of bullet points
% Non-reviewed

% 1.	Thompson KA. 2014. DNA Barcoding Enhances Vegetation Surveys. Barcode Bulletin 5(2). http://ibol.org/wp-content/uploads/2014/07/iBOL-Barcode-Bulletin-July-2014.pdf

\end{rSection}

\noindent\begin{rSection}{Scholarships and awards}

{\bf Dynamic Analysis of Buckling Restrained Braces}
\\The project aims at designing and fabrication of two Buckling Restrained Braces which were analyzed under dynamic loading. As alternative for conventional braces, these BRBs are also beneficial for seismic retro-fitting in RCC and steel structures.\\
\\{\bf Indirect Model Analysis of Structures}\\
Presented a Seminar on Indirect Model Analysis, explaining the method to compute response of Prototype from the Influence lines obtained from Model. Use of Muller Breslau Principle in Indirect Model Analysis and the Similitude between prototype and  model.\\

\\{\bf Microtunneling}\\
Presented a seminar on Micro Tunneling, explaining its advantages over conventional method of drainage laying systems. Analysis considering direct and indirect cost of micro tunneling was also discussed.

\end{rSection}
%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Technical Strengths}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Modeling and Analysis \ & AutoCad, Revit, StaadPro \\
Software \& Tools & MS Office, Latex \\
\end{tabular}

\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Work Experience}

\begin{rSubsection}{SJ Contracts, Pune}{June 2016}{Site Engineer}{}
\item On-site internship under this leading construction company. Learned and implemented various aspects such as quantity estimation, labour management and safety precautions.
\end{rSubsection}


\end{rSection}


%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Academic Achievements} 
 Runners up in B.G.Shirke Vidyarthi Competition for Innovative Project organized by Pune Construction Engineering Research Foundation in January 2018
\item Won First Prize in Model Making Competition Organized by Symbiosis Institute of Technology, Pune.
\end{rSection}

\newpage

%----------------------------------------------------------------------------------------
% Extra Curricular
%----------------------------------------------------------------------------------------
\begin{rSection}{Extra-Cirrucular} \itemsep -3pt
\item Co-Organized “ Nirmitee 2017” - a National Symposium of Civil Department of MIT, Pune
\item Attended a workshop on Autodesk Revit at IIT Bombay in 2014.
\item Winner of Inter Departmental Football Competition 2015.
\item Member of the  Rotaract Club Of Pune Pride from 2014 to 2017.
\item Worked for a start-up company Named OUST as a Regional Marketing Manager
%\item Trained and disciplined in National Cadet Corps (NCC), IIT Kanpur for a year.
 %\item  Participated in Vijyoshi Camp 2012 organized at Indian Institute of Science, Bangalore.
 %\item Won 2nd position in Kho-Kho in Intramurals conducted by Physical Education Section, IIT Kanpur.
 %\item Pursued French as second language during secondary school from Grade 6 to Grade 10. Also participated in French Song Competition and French G.K. Quiz in Class 10th. %

\end{rSection}

\begin{rSection}{Personal Traits}
\item Highly motivated and eager to learn new things.
\item Strong motivational and leadership skills.
\item Ability to work as an individual as well as in group.
\end{rSection}
\end{document}
